Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-14 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (5)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

1.-To clarify the figure 2, i recommend write "current" inside the figure, don't put just I.

@@

2.-This software model checking has performance in comparison the other commercials software,how is this performance?, Could you give the areas where your software performs better than commercial software?

@@

3.-In text reference at figure 1 the authors do not describe all symbols drawn into image, for instances, what is means G, T. I suspect that in section 4 they define which are the variables (Irradiation and temperature). I suggest you define those symbols in the text that that figure describes.

@@

4.- Are the verification results carried out affected by the different characteristics of the computers?

@@

The topic itself is interest for the PV application. However some section including abstract and result must be rewritten to be enhanced, here are the comments:

@@

\begin{resposta} 
We appreciate the comments and we realized that our text was not clear. As told for the Reviewer \#2, we should highlight that our main focus was at the validation process of the solar PV system, instead of the mathematical modelling that was investigated in prior studies over the last two decades. Moreover, we compare the results of using automated verification with simulation tool; real PV systems were just to check the validation results presented by the two tools. Because the automated verification and simulation tools are intended to be used during the project, before the buying or deployment of equipment. This information was carefully included at the revised Abstract, Introduction and at the Conclusion sections, because we concluded that was not clear in the previous version of the paper.

The authors have real load curve, and information collected from monitoring system of four (in five) PV systems/cases, however based on the fact that the automated verification is mathematical and not visual (curves/plots), seems that is not a adequate way of comparative.

The information from temperature and solar irradiance from every site, used to the simulation and formal verification tools, come from historical data collected from real stations that are available in Weather Base and Energy Plus web sites. Considering that the idea of the work is to show the effectiveness of the proposal just after the design phase, before deployment, seems that is plausible that procedure. Worth to mention that the sites from four case studies (the ones in a riverside indigenous community) do not have weather station available to collect data and the information must be approximated to Manaus data (the closet site with historic data).
\end{resposta}

-       Section 5 "Experimental Evolution" It can be changed to Verification result, otherwise the author should clarify the real measurements of the system.

@@

-       Can the author present the main waveform of the PV system in the steady state operation and under failure or any environmental change? waveforms such as: Input power, VMPP, IMPP, AC load

>>>>

(1) To clarify the figure 2, i recommend write "current" inside the figure, don't put just I.

@@

(2) This software model checking has performance in comparison the other commercials software,how is this performance?, Could you give the areas where your software performs better than commercial software?

@@

(3) In text reference at figure 1 the authors do not describe all symbols drawn into image, for instances, what is means G, T. I suspect that in section 4 they define which are the variables (Irradiation and temperature). I suggest you define those symbols in the text that that figure describes.

@@

(4) Are the verification results carried out affected by the different characteristics of the computers?

@@

(5) The topic itself is interest for the PV application. However some section including abstract and result must be rewritten to be enhanced, here are the comments:

@@

\begin{resposta} 
We appreciate these comments; we actually realized that our manuscript was unclear. We should highlight that our main research focus is on the validation process of the stand-alone solar PV system instead of the mathematical modelling, which was already investigated in prior studies over the last two decades. Moreover, we compare the results of using automated verification with simulation; real PV systems were employed just to validate the results presented by both approaches (model checking and simulation). Note that the automated verification and simulation tools are intended to be used during the design of the PV system, i.e., before actually buying or deploying the equipment. This information was carefully included in the revised abstract, introduction and conclusion sections since we concluded that it was unclear in the previous version of our manuscript.

The authors hold real load curve and information collected from monitoring system of four (in five) PV systems/cases \textcolor{red}{could you please identify them here? which one does not have such a information?}; however, based on the fact that the automated verification is mathematical and not visual (curves/plots), it seems that our comparison is not an adequate way \textcolor{red}{why not? explain the reason here}.

The information from temperature and solar irradiance from every site, used by the simulation and formal verification tools, come from historical data collected from real stations, which are available in Weather Base and Energy Plus web sites \textcolor{red}{shall we provide the website here?}. Considering that the idea of our study is to show the effectiveness of the proposed verification method just after the design phase (i.e., before deployment), we believe that it is a plausible procedure \textcolor{red}{to....}. Note that the sites from four case studies (i.e., the ones in a riverside indigenous community) do not have weather station available to collect data and the information must be approximated to Manaus data (the closest site with historical data) \textcolor{red}{what are the consequences? shall we state this limitation in the threats to validity section?}.
\end{resposta}

(6)      Section 5 "Experimental Evolution" It can be changed to Verification result, otherwise the author should clarify the real measurements of the system.

@@

(7)       Can the author present the main waveform of the PV system in the steady state operation and under failure or any environmental change? waveforms such as: Input power, VMPP, IMPP, AC load
